An efficient audio coding scheme for quantitative and qualitative large scale acoustic monitoring using the sensor grid approach

### 2017-10-17 paper/article.tex
References update

The identification of those sources from audio streams has been the subject of extensive research in the past for speech data \cite{anusuya2009}, music data \cite{tzanetakis2002}, and lately environmental data in which the current work falls. Studied classification methods are diverse, ranging from time-dependant modeling with hidden markov models \cite{ntalampiras2014} to "bag-of-frames" approaches \cite{aucouturier2007, foggia2015}. Common architectures include learning-based classifiers such as support vector machines \cite{kumar2016}, Gaussian mixture models \cite{radhakrishnan2005} or neural networks \cite{salamon2017, piczak2015}. Also, several type of features are considered to feed those classifiers. The most used are certainly spectral \cite{khunarsal2013} or cepstral \cite{couvreur2004} representations of the signal. Among them, Mel spectrograms and their cepstral-domain derivation, the Mel-frequency cepstrum coefficients (MFCC), arethe most widely used as of today. These representations effectively model the human cochlear response to sounds by grouping frequency components around critical bands in a logarithmic scale. While parameters are empirical and vary in the literature, a reference implementation includes 23.2~ms analysis and a 40 Mel bands resolution. The resulting representations are generally more densely sampled in time and frequency than in acoustic monitoring applications since acoustic indicators focus more scarce but very accurate measurements.

>>>>

The identification of those sources from audio streams has been the subject of extensive research in the past for speech data \cite{anusuya2009}, music data \cite{tzanetakis2002}, and lately environmental data in which the current work falls. Studied classification methods are diverse, ranging from time-dependant modeling with hidden markov models \cite{ntalampiras2014} to "bag-of-frames" approaches \cite{aucouturier2007, foggia2015}. Common architectures include learning-based classifiers such as support vector machines \cite{kumar2016}, Gaussian mixture models \cite{radhakrishnan2005} or neural networks \cite{salamon2017, piczak2015}. Also, several type of features are considered to feed those classifiers. The most used are certainly spectral \cite{khunarsal2013} or cepstral \cite{couvreur2004} representations of the signal. Among them, Mel spectrograms and their cepstral-domain derivation, the Mel-frequency cepstrum coefficients (MFCC), are the most widely used as of today. These representations effectively model the human cochlear response to sounds by grouping frequency components around critical bands in a logarithmic scale. The resulting representations are generally more densely sampled in time and frequency than in acoustic monitoring applications since acoustic indicators focus on more scarce but very accurate measurements.
